A Hierarchical Bayesian Framework for Exoplanetary Stellar Obliquity Distribution

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

We then apply the hierarchical Bayesian framework to all exoplanetary systems with sky-projected stellar obliquity $\lambda$ measurements. We use the sample of 161 systems summarized in \cite{Albrecht22} Table A1, which are predominantly Hot Jupiter systems. The inferred $\cos{\psi}$ distribution is shown in Figure~\ref{fig:psi_dist}. The $\cos{\psi}$ distribution peaks at 1 but is nearly flat between $-0.75$ and $0.75$ with no significant clustering. The distribution corresponds to an isotropic distribution of $\psi$ from $40\degr$ to $140\degr$. 
The aligned-system population dominates the distribution with a fraction of $w_0 = 0.67 \pm 0.09$. The hyperposteriors of the Beta distribution are $a_0 = 31.0\pm12.8$ and $b_0 = 0.40\pm0.12$.
The misaligned-system population has a fraction of $w_1 = 0.33 \pm 0.09$ and hyperposteriors of $a_1 = 1.56\pm0.93$ and $b_1 = 1.64\pm1.58$.

@@

Our analysis suggests misaligned systems have nearly isotropic stellar obliquity distribution. When comparing the inferred distribution with the prediction of stellar obliquity distributions in different Hot Jupiter origin scenarios, it is in best agreement with the outcome of the scattering of multiple giant planets after a convergent disk migration \citep[e.g.,][]{Beague12}, which could produce planets with orbital inclination from $0\degr$ to $180\degr$ with a peak at $0\degr$. This interesting result can be further tested on more carefully selected Hot Jupiter samples and put constraints on Hot Jupiter origins.

>>>>

We then apply the hierarchical Bayesian framework to all exoplanetary systems with sky-projected stellar obliquity $\lambda$ measurements. We use the sample of 161 systems summarized in \cite{Albrecht22} Table A1, which are predominantly Hot Jupiter systems. The inferred $\cos{\psi}$ distribution is shown in Figure~\ref{fig:psi_dist}. The $\cos{\psi}$ distribution peaks at 1 but is nearly flat between $-0.75$ and $0.75$ with no significant clustering. The distribution corresponds to a pile-up of planets with stellar obliquity less than $40\degr$ and an isotropic distribution of planets with stellar obliquity from $40\degr$ to $140\degr$. 
The aligned-system population dominates the distribution with a fraction of $w_0 = 0.67 \pm 0.09$. The hyperposteriors of the Beta distribution are $a_0 = 31.0\pm12.8$ and $b_0 = 0.40\pm0.12$.
The misaligned-system population has a fraction of $w_1 = 0.33 \pm 0.09$ and hyperposteriors of $a_1 = 1.56\pm0.93$ and $b_1 = 1.64\pm1.58$.

@@

Our model identifies a pile-up of systems with stellar obliquity less than $40\degr$ and finds that misaligned systems have nearly isotropic stellar obliquity distribution. When comparing the inferred distribution with the prediction of stellar obliquity distributions in different Hot Jupiter origin scenarios, it is in best agreement with the outcome of the scattering of multiple giant planets after a convergent disk migration \citep[e.g.,][]{Nagasawa11, Beague12}. This particular intriguing result should be further examined on more carefully selected Hot Jupiter samples and put constraints on Hot Jupiter origin channels.
